```{r, echo = FALSE}
library(raster)
library(dplyr)
library(ggplot2)
library(metafor)
library(nlme)
library(gridExtra)
library(broom)

source('02_functions.R')

fl_combined <- readr::read_csv("Data_outputs/fl_combined.csv")

event <- filter(fl_combined, Event == 'Yes')
no_event <- filter(fl_combined, Event != 'Yes')

```

The log ratio is the natural logarithm of the proportion of change in species richness (ln(final richness / initial richness)). We calculate the percent change in species richness as exp(log ratio) = final richness / initial richness. 

```{r, echo = FALSE, eval = FALSE}
# Log ratio reference for me
# When there is no change in richness, final / initial = 1
log(1) = 0

# Example: 50% increase in richness between time points
# When richness increases over time, final / initial > 1
log(150 / 100)
0.4054651
# Percent change = exp(log ratio) - 1
exp(0.4054651) - 1

# Example: 50% decrease in richness between time points
# When richness decreases over time, final / initial < 1
log(50 / 100)
[1] -0.6931472
# Percent change = exp(log ratio) - 1
exp(-0.6931472) - 1
```

To test whether local marine species richness has changed over time, we have performed a meta-regression on the relationship between the log ratio of species richness between the final and initial time points and study duration. The weighted analysis included 213 sites and 50 studies while the unweighted analysis included 505 sites and 122 studies.  

In the both the weighted and unweighted analyses, species richness did not change on average (mod1, mod2), nor was there a relationship between change in species richness and duration (mod1).

```{r}
# Weighted analysis - and naive model plot
mod1 <- 
  rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, 
         data = filter(fl_combined, !is.na(yi.SppR.ROM) & !is.na(vi.SppR.ROM) & 
                       vi.SppR.ROM > 0),
         random = ~ 1 | as.factor(Study.ID), 
         mods = ~ Duration)
mod1

mod2 <- 
  rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, 
         data = filter(fl_combined, !is.na(yi.SppR.ROM) & !is.na(vi.SppR.ROM) & 
                       vi.SppR.ROM > 0),
          random = ~ 1 | as.factor(Study.ID))
mod2

# Unweighted analysis that includes all of the log ratios that do not have 
# variance associated with them. 
lme1 <- lme(yi.SppR.ROM ~ Duration, random = ~ 1 | Study.ID, data = fl_combined, 
            na.action = na.omit)
summary(lme1)
```

Looking at the caterpillar plot for each of the studies, it is probably best to keep Study.ID as a random effect.

```{r, echo = FALSE, eval = FALSE}
# something is wrong with this plot righ tnow
lattice::dotplot(ranef(lme1, condVar=TRUE), cex = 0.5, scales=list(cex=0.4))
```

```{r, fig.height=7.5, fig.width=6.7}
duration_w <- 
filter(fl_combined, !is.na(yi.SppR.ROM) & !is.na(vi.SppR.ROM) & vi.SppR.ROM > 0) %>%
ggplot(data = ., aes(x = Duration, y = yi.SppR.ROM, colour = as.factor(Study.ID))) +
  geom_point(size = 1) + 
  ylab('Log Ratio') +
  theme_bw() +
  theme(legend.position = 'none') +
  geom_hline(yintercept = 0, colour = 'red', linetype = 'dashed') +
  ggtitle('Weighted Analysis') + 
  xlab('Duration (years)') #+
  #ylim(-2, 2)

duration_uw <- 
filter(fl_combined, !is.na(yi.SppR.ROM)) %>%
ggplot(data = ., aes(x = Duration, y = yi.SppR.ROM, colour = as.factor(Study.ID))) +
  geom_point(size = 1) + 
  ylab('Log Ratio') +
  theme_bw() +
  theme(legend.position = 'none') +
  geom_hline(yintercept = 0, colour = 'red', linetype = 'dashed') +
  ggtitle('Unweighted Analysis') + 
  xlab('Duration (years)') #+
  #ylim(-3, 3)

grid.arrange(duration_w, duration_uw, nrow = 2)

```

Both the weighted and unweighted naive models, where duration is the only predictor, show no significant change in species richness on average.  

In the short term, negative and uncertain events were associated with increases in species richness. On average this was increase was 39% and 32% for a study associated with a positive and uncertain event, respectively.

Long term? Studies associated with events expected to be positive or uncertain were found to have a decline in richess? 5 - 1% per year? This doesn't make a ton of sense.

```{r}
# Confirm that the events are being matched with the data properly #
localmod <- 
  rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = event,
         random = ~ 1 | factor(Study.ID),
         mods = ~ Duration:expected_change + expected_change + 0)
localmod

get_percent_change(localmod$b)

ggplot(data = event, aes(x = Duration, y = yi.SppR.ROM)) + 
  geom_point(aes(colour = expected_change)) + 
#  ylim(c(-2.1, 2.1)) + 
  stat_smooth(method = 'lm', aes(colour = expected_change))


local2U <- lme(yi.SppR.ROM ~ Duration:expected_change + expected_change + 0, 
               random = ~ 1 | factor(Study.ID), data=event, na.action = na.omit)
summary(local2U)

#event_dir_summ_df <- 
 # mk_rma_summary_df(original_df = event, rma_object = local2, categorical = TRUE)

row.names(event_dir_summ_df) <- c(' Negative', ' Positive', ' Uncertain', 
                                  ' D*Negative', ' D*Positive', 
                                  ' D*Uncertain')

# The short term effect of events
ggplot(data = event_dir_summ_df[1:3, ]) +
  geom_point(aes(x = row.names(event_dir_summ_df[1:3, ]), y = mean_estimate)) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci, 
                    x = row.names(event_dir_summ_df[1:3, ]), width = 0)) +
  theme_bw() + 
  ylab('Change in log ratio / year\n') +
  xlab('\nEvent Type\n') + 
  theme(panel.grid.major  = element_blank(),
        panel.grid.minor  = element_blank()) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = 'yellow') +
  ylim(c(-0.75, 0.75)) +
  scale_x_discrete(labels = paste(row.names(event_dir_summ_df[1:3, ]), "\n k = ", as.character(event_dir_summ_df[1:3, ]$studies_per_mod), "\n n = ", as.character(event_dir_summ_df[1:3, ]$sites_per_mod)))

# The long term effect of events:
ggplot(data = event_dir_summ_df[4:6, ]) +
geom_point(aes(x = row.names(event_dir_summ_df[4:6, ]), y = mean_estimate)) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci, 
                    x = row.names(event_dir_summ_df[4:6, ]), width = 0)) +
  theme_bw() + 
  ylab('Change in log ratio / year\n') +
  xlab('\nEvent Type\n') + 
  theme(panel.grid.major  = element_blank(),
        panel.grid.minor  = element_blank()) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = 'yellow') +
  ylim(c(-0.1, 0.1)) +
  scale_x_discrete(labels = paste(row.names(event_dir_summ_df[4:6, ]), "\n k = ", as.character(event_dir_summ_df[4:6, ]$studies_per_mod), "\n n = ", as.character(event_dir_summ_df[4:6, ]$sites_per_mod)))


```

What sample sizes do we have for this local even dataset? The weighted analysis is done using 27 negative events, 19 positive events, and 14 uncertain events.

```{r}
filter(event, !is.na(yi.SppR.ROM) & !is.na(vi.SppR.ROM) & vi.SppR.ROM > 0) %>%
  count(., expected_change)

```

In the unweighted model there is no significant effect of event except in those studies for which an exepcted change direction was unclear. In these studies there was a decline in species in long term studies of about -1% per year. 

Clarify: -1% change in ther ate of change -> this is the duration effect alone? From log_ratio ~ Duration?

```{r}
local_lme <- 
  lme(yi.SppR.ROM ~ Duration:expected_change + expected_change + 0, 
      random = ~ 1 | factor(Study.ID), 
      data = event, na.action = na.omit)
summary(local_lme)

get_percent_change(local_lme$coefficients$fixed)
```

In the subset of studies for which no events were explicitly documented, cumulative human impacts were associated with immediate declines. On average when mean impact was zero, species declined by 4.8%. For each unit of cumulative human impact (global range = ~0 - 11.1 (need to double check this value); from our study range = 0.26 - 9.5), our results show that the rate of species loss increases by 7.5%. However, as study duration increases, the effect of mean impact on the rate of change in species richness is actually positive. Cumulative human impact moderates the rate of change in richness by 1 % per year. (Does this mean that each year the rate of change in richness is: -4.8% * 1.2)

Does this conflict at all with the fact that duration * events have the opposite effect as we expected?

```{r}
global1 <- 
  rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, 
         data = no_event,
         random = ~ 1 | Study.ID, 
         mods = ~ Duration * mean_imps)
global1

get_percent_change(global1$b)
```


```{r}
global2 <- 
  rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, 
         data = fl_combined,
         random = ~ 1 | Study.ID, 
         mods = ~ Duration * mean_imps)
global2


global_summ_df <- 
  mk_rma_summary_df(no_event, rma_object = global1)

filter(no_event, !is.na(yi.SppR.ROM) & !is.na(vi.SppR.ROM) & 
                     vi.SppR.ROM > 0 & !is.na(mean_imps)) %>%
  distinct(Site) %>%
  count(.)

row.names(global_summ_df) <- c('Intercept', 'Duration', 'Human Impact', 
                                'Duration*Human Impact')
global_summ_df$predictors <- factor(row.names(global_summ_df), levels = c('Intercept', 'Duration', 'Human Impact', 'Duration*Human Impact'))

ggplot(data = global_summ_df) +
  geom_point(aes(x = mean_estimate, y = predictors), 
             size = 4, colour = 'white') +
  geom_errorbarh(aes(x = mean_estimate, xmin = lower_ci, xmax = upper_ci, 
                    y = predictors, height = 0), colour = 'white', 
                    size = 1) + 
  theme_wb() + 
  xlab('Mean Effect Size\n') +
  ylab('\nPredictor') + 
  theme(axis.title.x = element_text(vjust = -0.5, size = 16), 
        axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(vjust = 1.5, size = 16), 
        panel.grid.major  = element_blank(),
        panel.grid.minor  = element_blank()) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = 'yellow')
  #xlim(c(-8, 8))


global_lme <- 
filter(fl_combined, !is.na(yi.SppR.ROM) & !is.na(vi.SppR.ROM) & 
                     vi.SppR.ROM > 0 & !is.na(mean_imps)) %>%
  lme(yi.SppR.ROM ~ Duration * scale(mean_imps), random = ~ 1 | factor(Study.ID),
      data = .)
summary(global_lme)


global2 <- 
filter(fl_combined, !is.na(yi.SppR.ROM) & !is.na(vi.SppR.ROM) & 
                     vi.SppR.ROM > 0 & !is.na(mean_imps)) %>%
    rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM,
          data = ., 
          random = ~ 1 | Study.ID, 
          mods = ~ Duration * (mean_lin_change + mean_invs +  mean_nuts)
)
global2

global_summ_df <- 
  mk_rma_summary_df(fl_combined, rma_object = global2)
```

does it matter that for short term studies the linear change is essentially the absolute change?

```{r}
row.names(global_summ_df) <- c('Intercept', 'Duration', 'Climate Velocity', 
                               'Linear Temp Change', 'Invasive Potential', 
                               'Pesticides', 'Nutrients', 
                                'Duration*Climate Velocity', 
                                'Duration*Linear Temp Change', 
                                'Duration*Invasive Potential', 
                                'Duration*Pesticides', 
                                'Duration*Nutrients')
global_summ_df$predictors <- factor(row.names(global_summ_df), levels = c(
                               'Intercept', 'Duration', 'Climate Velocity', 
                               'Linear Temp Change', 'Invasive Potential', 
                               'Pesticides', 'Nutrients', 
                                'Duration*Climate Velocity', 
                                'Duration*Linear Temp Change', 
                                'Duration*Invasive Potential', 
                                'Duration*Pesticides', 
                                'Duration*Nutrients'))


ggplot(data = global_summ_df[-c(6, 7), ]) +
  geom_point(aes(x = mean_estimate, y = predictors), 
             size = 4, colour = 'white') +
  geom_errorbarh(aes(x = mean_estimate, xmin = lower_ci, xmax = upper_ci, 
                    y = predictors, height = 0), colour = 'white', 
                    size = 1) + 
  theme_wb() + 
  xlab('Mean Effect Size\n') +
  ylab('\nPredictor') + 
  theme(axis.title.x = element_text(vjust = -0.5, size = 16), 
        axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(vjust = 1.5, size = 16), 
        panel.grid.major  = element_blank(),
        panel.grid.minor  = element_blank()) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = 'yellow')
  #xlim(c(-8, 8))

# Wait, what do you do about high VIFs when working with interaction effects? 

global2_lme <- 
lmer(yi.SppR.ROM ~ Duration * (scale(mean_vocc) + scale(mean_lin_change) + scale(mean_invs)  + scale(mean_nuts)) + (1 | Study.ID), data = fl_combined)
summary(global2_lme)
# scaling?

# testing for multicollinearity using vif (modified for class lmerMod)
# http://jonlefcheck.net/2012/12/28/dealing-with-multicollinearity-using-variance-inflation-factors/
vif.lme <- function (fit) {
    ## adapted from rms::vif
    v <- vcov(fit)
    nam <- names(fixef(fit))
    ## exclude intercepts
    ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
    if (ns > 0) {
        v <- v[-(1:ns), -(1:ns), drop = FALSE]
        nam <- nam[-(1:ns)] }
    d <- diag(v)^0.5
    v <- diag(solve(v/(d %o% d)))
    names(v) <- nam
    v }

vif.lme(global2_lme)


# Look at this now
cor()

```

Warning message:  
Some predictor variables are on very different scales: consider rescaling   

can rescale - change by magnitude of 10 or 100 or 1000 or whatever - then go back 
and compare with the original test to make sure that the coefficients are identical,
but just off by whatever magnitude that you rescaled by

interactions - high VIF 
- can centre values (values that are really big are more likely to be highly collinear
  )
- if the results don't change ok then you can continue to run with the rescaled values

- predicts doesn't account for centering...

- wrapper function - need to centre values before putting them into the prediction
- the expected y values won't change depending on centred vs. not centred - even though 
the coefficients will be different between a model with raw vs. centred values

f(x1, x2) {
  X1A = x1 = x_bar1
  X2A = x2 = x_bar2

pred(mod, df[x1A, x2A])

}



- centering everything
- some people scale everything (z - scoring) 




### Making the prediction map for the combination of multiple smaller layers

```{r}
extra_impact_dir <- '/Users/jillian/R_projects/Human_Cumulative_Impacts/Data'

invasives <- raster(paste0(extra_impact_dir, '/invasives_raw/invasives.tif'))
fertilizers <- raster(paste0(extra_impact_dir, '/plumes_fertilizer_raw/plumes_fert.tif'))
pesticides <- raster(paste0(extra_impact_dir, '/plumes_pesticide_raw/plumes_pest.tif'))


yr_min <- min(fl_combined$T1)
yr_max <- max(fl_combined$T2)

hadrast <- loadHadSST1('master_data/', hadsstFilename = "HadISST_sst.nc")
all_rasters <- getAllRasters(hadrast, years = yr_min:yr_max)
#velocity <- getVelocityMag_raster(hadsst_raster, years = yr_min:yr_max)
#linear <- getSSTLinChangeRaster(hadsst_raster, years = yr_min:yr_max)

velocity <- selectRaster(all_rasters, 'Velocity')
linear <- selectRaster(all_rasters, 'LinearChange')
beep()



# Create cropped raster

#(xmin, xmax, ymin, ymax)

# smaller extent
e <- as(extent(-71.705531, -67.944214, 41.377132, 43.180299), 
       'SpatialPolygons')

# boston harbour extent
e <- as(extent(-71.085674, -70.581677, 42.196429, 42.544938), 'SpatialPolygons')

# east coast
e <- as(extent(-71.254492, -69.784015, 40.963025, 43.861433), 'SpatialPolygons') 

# bigger extent I can look at
e <- as(extent(-76.998293, -36.612552, 31.445744, 52.414631), 
       'SpatialPolygons')

proj4string(e) <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

e <- spTransform(e, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))

crop_inv <- crop(invasives, e)
crop_fert <- crop(fertilizers, e)
crop_pest <- crop(pesticides, e)

par(mfrow = c(1, 3))
plot(crop_inv)
plot(crop_fert)
plot(crop_pest)


e <- spTransform(e, CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
crop_vel <- crop(velocity, e)
crop_lin <- crop(linear, e)

crop_vel <- projectRaster(from = crop_vel, crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs")
crop_lin <- projectRaster(from = crop_lin, crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs")

crop_vel <- resample(crop_vel, crop_inv)
crop_lin <- resample(crop_lin, crop_inv)
crop_fert <- resample(crop_fert, crop_inv)
crop_pest <- resample(crop_pest, crop_inv)

test <- crop_inv

x <- as.array(crop_inv)

switch_NA_zero <- function(cell) {
  cell <- cell
  if (is.na(cell)) {
    cell <- 0
  } else if (cell == 0) {
    cell <- NA
  }
  return(cell)
} 

y <- apply(x, MARGIN = c(1, 2), FUN = switch_NA_zero)

z <- raster(x = y, template = crop_inv)
plot(z)

crop_inv2 <- z


for (i in list(crop_inv2, crop_fert, crop_pest, crop_vel, crop_lin)) {
  print(names(i))
  print(extent(i))
  print(origin(i))
}

par(mfrow = c(1, 2))
plot(crop_vel)
plot(crop_lin)

beep()

# Create raster layers for different durations 
time_map1 <- !is.na(crop_vel)

names(time_map1) <- 'Duration'
time_map10 <- time_map1 * 10
time_map20 <- time_map1 * 20
time_map50 <- time_map1 * 50


# Create a raster stack with the predictor layers
# Duration1
# Cumulative Impacts

# make sure the names of the raster layers match up with the names used in the model

names(global2_lme@frame)

names(crop_vel) <- 'mean_vocc'
names(crop_lin) <- 'raster_lin'
names(crop_inv2) <- 'mean_invs'
names(crop_fert) <- 'mean_fert'
names(crop_pest) <- 'mean_pest'


multi_preds <- stack(time_map1, crop_vel, crop_lin, crop_inv2, crop_fert, crop_pest)

# re.form: formula for random effects to condition on.  If 'NULL', include all 
# random effects; if 'NA' or '~0', include no random effects
predict1 <- predict(multi_preds, global2_lme, fun = lme4:::predict.merMod, re.form=~0)
beep()

predict1_percent <- (exp(predict1) - 1) * 100

plot(predict1, col = heat.colors(100), colNA = 'black')

plot(predict1_percent, col = heat.colors(100), colNA = 'black')

plot(predict1_percent, col = rainbow(100))



multi_preds <- stack(time_map10, crop_vel, crop_lin, crop_inv2, crop_fert, crop_pest)

# re.form: formula for random effects to condition on.  If 'NULL', include all 
# random effects; if 'NA' or '~0', include no random effects
predict1 <- predict(multi_preds, global2_lme, fun = lme4:::predict.merMod, re.form=~0)
beep()

predict1_percent <- (exp(predict1) - 1) * 100

plot(predict1, col = rainbow(100))

plot(predict1, col = topo.colors(100))

plot(predict1_percent, col = heat.colors(3))

plot(predict1_percent, col = rainbow(255))

```




The log ratio is the log of the proportion of change in species richness over time. If the log ratio = 0.1, 

log(SppR2 / SppR1) = LR

LR ^ e = SppR2 / SppR1

> exp(-0.13)
[1] 0.8780954

> exp(-0.14)
[1] 0.8693582


exp(0.13) - 1

exp(-0.13) - 1

predict1_percent <- exp(predict1) - 1


```{r}
# Create raster layers for different durations 
time_map1 <- imp_map > 0
names(time_map1) <- 'Duration'
beep()

time_map10 <- time_map1 * 10
time_map20 <- time_map1 * 20
time_map50 <- time_map1 * 50


# Create a raster stack with the predictor layers
# Duration1
# Cumulative Impacts

# make sure the names of the raster layers match up with the names used in the model

names(global_lme@frame)

names(imp_map) <- 'mean_imps'
imp_preds <- stack(time_map1, imp_map)

# re.form: formula for random effects to condition on.  If 'NULL', include all 
# random effects; if 'NA' or '~0', include no random effects
predict1 <- predict(imp_preds, global_lme, fun = lme4:::predict.merMod, re.form=~0)

plot(predict1)


```




the log proportional change in the means of a treatment and control group.

# Including an intercept changes the outcome of the results where there is a 
# decline on average over time, but there is no relationship between event 
# categories and log ratio.
# Including duration as an interaction with expected change direction has no 
# effect on the direction of the response.

global1 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_imps + 1)

global2 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_vocc + 1)

global3 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_imps + mean_vocc + 1)

global4 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration:mean_imps + Duration:mean_vocc + 1)

global5 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_imps + raster_lin + 1)

global6 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_invs + raster_lin + 1)

global7 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_invs + mean_vocc + 1)




global8 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = no_event,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_imps + 1)

global9 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = no_event,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_vocc + 1)

global10 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = no_event,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_imps + mean_vocc + 1)

global11 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = no_event,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration:mean_imps + Duration:mean_vocc + 1)

global12 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = no_event,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_imps + raster_lin + 1)

global13 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = no_event,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + mean_invs + raster_lin + 1)

global14 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = no_event,
       random = ~ 1 | factor(Study.ID),
       mods   = ~ Duration + Duration*mean_invs + mean_vocc + 1)


# Unweighted
lme1 <- lme(yi.SppR.ROM ~ Duration + 1, random = ~ 1 | factor(Study.ID), weights = NULL, control=lmeControl(sigma = 1), data=data, na.action = na.exclude)
summary(lme1)

lme2 <- lme(yi.SppR.ROM ~ Duration - 1, random = ~ 1 | factor(Study.ID), weights = NULL, control=lmeControl(sigma = 1), data=data, na.action = na.exclude)
summary(lme2)


local_lme1 <-
  lme(yi.SppR.ROM ~ Duration - 1 , random = ~ 1 | factor(Study.ID), weights = NULL, control=lmeControl(sigma = 1), data=data, na.action = na.exclude)
summary(lme1)


rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = event,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration:factor(expected_change) - 1)

local_lme2 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = event,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration + factor(expected_change) - 1)

local_lme3 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = event,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration + factor(expected_change) - 1)

local_lme4 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = event,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration + factor(expected_change) + 1)





res.lme <- lme(yi.SppR.ROM ~ Duration + 1, random = ~ 1 | factor(Study.ID), weights = NULL, control=lmeControl(sigma = 1), data=no_event, na.action = na.exclude)
summary(res.lme)

event.lme <- lme(yi.SppR.ROM ~ Duration + expected_change - 1, random = ~ 1 | factor(Study.ID), weights = NULL, control=lmeControl(sigma = 1), data=event, na.action = na.exclude)
summary(event.lme)


mod1 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID))

mod2 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration + 1)

mod3 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration - 1)





# use a weighting that is based on sample size

# power analysis and compare with and without variance weight

# linear model - plain - is unweighted
# linear model - assign weight argument (will make it weighted) - relative to the maximum weighting
# variance weighted meta-analysis is different - because it's operating from the fact that you know the variance surrounding each study around the 

# sample size weighted 


# Result #1 
# Let's do it like everyone else
# 1.2% decrease per year - it's negative
# Naive analysis:
mod1 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration + 1)

ggplot(data = data, aes(x = Duration, y = yi.SppR.ROM, colour = as.factor(Study.ID))) +
  geom_point(size = 3) + 
  ylab('Log Ratio') +
  #theme_wb() +
  theme(axis.text = element_text(size = 16), 
        axis.title = element_text(size = 18), 
        legend.position = 'none') + 
  #geom_abline(intercept = -0.0112, slope = -0.0084, colour = 'white', lwd = 1.5) +
  geom_hline(y = 0, colour = 'red', linetype = 'dashed')

# Result #2
#- lets look at the ecological 
#- oh look, this matches our expectations
#- event types model: 
#- how did we get these, expected change directions

mod2 <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = event,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration:factor(expected_change) - 1)

mod2_summ_df <- 
  mk_summary_df(event, rma_object = mod2, moderators = FALSE, 
                mods = 'expected_change')
row.names(mod2_summ_df) <- c(' Duration*Negative', ' Duration*Positive', ' Duration*Uncertain')

event_counts <- ddply(event[which(event$rich_ROM_w == 1), ], .(expected_change), summarise, 'studies' = length(unique(Study.ID)), 'sites' = length(unique(id)))
rownames(event_counts) <- c('Duration*Negative', 'Duration*Positive', 'Duration*Uncertain')


mod3 <- rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = no_event,
               random = ~ 1 | factor(Study.ID),
               mods = ~ Duration - 1)

mod3_summ_df <- 
  mk_summary_df(no_event, rma_object = mod3, moderators = FALSE)
studies <- length(unique(no_event[which(no_event$rich_ROM_w == 1), ]$Study.ID))
sites <- length(no_event[which(no_event$rich_ROM_w == 1), ]$id)
rownames(mod3_summ_df) <- ' Duration'

noevent_counts <- data.frame('studies' = studies, 'sites' = sites)
noevent_counts

x <- rbind(mod2_summ_df, mod3_summ_df)
x$studies_per_mod[1:3] <- as.vector(unlist(event_counts['studies']))
x$studies_per_mod[4] <- as.vector(unlist(noevent_counts['studies']))
x$sites_per_mod[1:3] <- as.vector(unlist(event_counts['sites']))
x$sites_per_mod[4] <- as.vector(unlist(noevent_counts['sites']))

all <- x
all$predictors <- factor(rownames(all), levels = c(' Duration', ' Duration*Uncertain', ' Duration*Positive', ' Duration*Negative'), ordered = TRUE)
all$predictors <- factor(all$predictors, levels=rev(levels(all$predictors)))

# plot
ggplot(data = all) +
  geom_point(aes(y = factor(predictors), x = mean_estimate), size = 4, colour = 'white') +
  geom_errorbarh(aes(x = mean_estimate, xmin = lower_ci, xmax = upper_ci, 
                    y = factor(predictors), height = 0), size = 1, colour = 'white') +
  theme_wb() + 
  xlab('Change in log ratio/year\n') +
  ylab('\nEvent Type\n') + 
  theme(axis.text.x = element_text(size = 18), 
        axis.text.y = element_text(size = 18, hjust = 0), 
        axis.title.y = element_text(vjust = 1.6, size = 20),
        axis.title.x = element_text(vjust = -0.5, size = 20), 
        panel.grid.major  = element_blank(),
        panel.grid.minor  = element_blank()) +
  geom_vline(y = 0, linetype = "dashed", colour = 'yellow') +
  xlim(c(-0.12, 0.12)) +
  scale_y_discrete(labels = paste(all$predictors, "\n studies = ", as.character(all$studies), "\n sites = ", as.character(all$sites)))


# Unweighted

res.lme <- lme(yi.SppR.ROM ~ Duration + 1, random = ~ 1 | factor(Study.ID), weights = NULL, control=lmeControl(sigma = 1), data=no_event, na.action = na.exclude)
summary(res.lme)

event.lme <- lme(yi.SppR.ROM ~ Duration + expected_change - 1, random = ~ 1 | factor(Study.ID), weights = NULL, control=lmeControl(sigma = 1), data=event, na.action = na.exclude)
summary(event.lme)




# Result #3
# In this model I include climate velocity - which I do not think should 
# interact with duration. In a model with absolute temperature change alone, I
# would include the effect of duration.

global_model <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ mean_imps + Duration:mean_imps + Duration + SppR1 + Duration:mean_vocc + 1)

global_model <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ mean_imps + Duration + SppR1 + mean_vocc + 1)


global_model <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ scale(mean_imps) + scale(Duration):scale(mean_imps) + scale(Duration) + scale(SppR1) + scale(Duration):scale(mean_vocc) + 1)


global_model <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration:mean_imps + Duration + SppR1 + raster_lin + Duration:raster_lin + 1)



global_model <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration:mean_imps + Duration + SppR1 + Duration:vel_decade + 1)

# Why not include a model where duration is not being included
velocity_model <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration + vel_decade + 1)

imps_model <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | factor(Study.ID),
       mods = ~ Duration + mean_imps + 1)





global_model <- 
rma.mv(yi = yi.SppR.ROM, V = vi.SppR.ROM, data = data,
       random = ~ 1 | Study.ID,
       mods = ~ Duration:mean_imps + Duration + SppR1 + Duration*temp_changes+1)


global_summ_df <- 
  mk_summary_df(data, rma_object = global_model, moderators = FALSE, 
                mods = c('mean_imp_vals', 'Duration', 'vel_decade'))
row.names(global_summ_df) <- c('Intercept', 'Human Impact', 'Duration', 
                               'Initial Richness', 'Climate Velocity')
global_summ_df$predictors <- factor(row.names(global_summ_df), levels = c('Intercept', 'Duration', 'Initial Richness', 'Climate Velocity', 'Human Impact'))

global_summ_df <- global_summ_df[-which(global_summ_df$predictors == 'Intercept'), ]

ggplot(data = global_summ_df) +
  geom_point(aes(x = mean_estimate, y = predictors), 
             size = 4, colour = 'white') +
  geom_errorbarh(aes(x = mean_estimate, xmin = lower_ci, xmax = upper_ci, 
                    y = predictors, height = 0), colour = 'white', 
                    size = 1) + 
  theme_wb() + 
  xlab('Mean Effect Size\n') +
  ylab('\nPredictor') + 
  theme(axis.title.x = element_text(vjust = -0.5, size = 16), 
        axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(vjust = 1.5, size = 16), 
        panel.grid.major  = element_blank(),
        panel.grid.minor  = element_blank()) +
  geom_vline(y = 0, linetype = "dashed", colour = 'yellow') +
  xlim(c(-0.07, 0.07))


# HCI map, linear change, and climate velocities
library(rasterVis)

my_theme <- rasterTheme(region = colorRampPalette(c("blue","white", "red")),
#alpha=0.6,
panel.background = list(col = 'black')
)

rasterTheme

col_theme <- colorRampPalette(c("blue","white", "red"))
col_theme$panel.background$col = 'black' 

levelplot(linear, col.regions = pal(101), at = seq(-0.3, 0.3, length.out = 101))