```{r, echo = FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(metafor)
library(lme4)
library(lmerTest)
library(ggplot2)

source('02_functions.R')

fl_combined <- readr::read_csv("../Data_outputs/fl_combined.csv") %>% 
  mutate(Study.ID = factor(Study.ID))

event <- filter(fl_combined, Event == 'Yes')
no_event <- filter(fl_combined, Event != 'Yes')

```

To test whether local marine species richness has changed over time, we have performed a meta-regression on the relationship between the log ratio of species richness between the final and initial time points and study duration. The weighted analysis included 212 sites from 50 studies while the unweighted analysis included 704 sites and 147 studies.  

In the both the weighted and unweighted analyses, species richness did not change on average (mod1, mod2), nor was there a relationship between change in species richness and duration (mod1).


#### Human Impacts

When we consider how human impacts may affect species richness

```{r}

hci_rma_all <- 
  rma.mv(yi = yi_SppR_ROM, V = vi_SppR_ROM, 
         data = fl_combined, 
         random = ~ 1 | Study.ID, 
         mods = ~ Duration*mean_imps)
hci_rma_all


mk_rma_summary_df(hci_rma_all) %>%
  filter(driver != 'intrcpt') %>% 
  mutate(driver = factor(driver, levels = c('Duration:mean_imps', 'Duration', 'mean_imps'))) %>%
  ggplot(data = ., aes(x = estimate, y = driver)) + 
    theme_bw() +
    geom_errorbarh(aes(xmin = ci_lb, xmax = ci_ub), height = 0, size = 1.5) + 
    geom_point(size = 4) + 
    geom_vline(xintercept = 0, colour = 'black', linetype = 'dashed') + 
    xlim(c(-0.09, 0.09)) + 
    theme(axis.text.y = element_text(hjust = 1, size = 20), 
          axis.text.x = element_text(size = 20), 
          axis.title = element_text(size = 20))

```

* Note: the response to human impacts is different if we exclude the data containing the studies associated with events (signs reverse)


```{r}

hci_rma_ne <- 
  rma.mv(yi = yi_SppR_ROM, V = vi_SppR_ROM, 
         data = no_event, 
         random = ~ 1 | Study.ID, 
         mods = ~ Duration*mean_imps)
hci_rma_ne

mk_rma_summary_df(hci_rma_all) %>%
  mutate(driver = gsub("mean_imps", "Human Impact", driver)) %>%
  filter(driver != 'intrcpt') %>% 
  mutate(driver = factor(driver, levels = c('Duration:Human Impact', 'Duration', 'Human Impact'))) %>%
  ggplot(data = ., aes(x = estimate, y = driver)) + 
    theme_bw() +
    geom_errorbarh(aes(xmin = ci_lb, xmax = ci_ub), height = 0, size = 1.5) + 
    geom_point(size = 4) + 
    geom_vline(xintercept = 0, colour = 'black', linetype = 'dashed') + 
    xlim(c(-0.09, 0.09)) + 
    theme(axis.text.y = element_text(hjust = 1, size = 20), 
          axis.text.x = element_text(size = 20), 
          axis.title = element_text(size = 20)) + ylab("")

```

#### Full drivers model

```{r}

full_rma_all <- 
    rma.mv(yi = yi_SppR_ROM, V = vi_SppR_ROM,
           data = fl_combined %>% mutate(scaled_invs = mean_invs * 10^-3),
          random = ~ 1 | Study.ID, 
          mods = ~ Duration * SppR1 * (sliced_vocc + mean_nuts + scaled_invs)
)
full_rma_all

full_rma_all_summary <- 
mk_rma_summary_df(full_rma_all) %>% 
  #standardise_coefs(.) %>% 
  filter(driver != 'intrcpt') %>% 
  #filter(sig_stars != ' ') %>% 
  mutate(grouping = as.character(driver)) %>% 
  mutate(grouping = replace(grouping, grouping %in% c('SppR1', 'Duration', 'Duration:SppR1'), 'mods')) %>% 
  mutate(grouping = replace(grouping, grouping %in% c('sliced_vocc', 'SppR1:sliced_vocc',
        'Duration:sliced_vocc', 'Duration:SppR1:sliced_vocc'), 'vocc'), 
         grouping = replace(grouping, grouping %in% c('mean_nuts', 
        'SppR1:mean_nuts', 'Duration:mean_nuts', 'Duration:SppR1:mean_nuts'), 'nuts'), 
         grouping = replace(grouping, grouping %in% c('scaled_invs', 
        'SppR1:scaled_invs', 'Duration:scaled_invs', 'Duration:SppR1:scaled_invs'), 'invs')) %>% 
  mutate(driver = factor(driver, levels = c('Duration:SppR1', 'Duration', 'SppR1', 
                                   'Duration:SppR1:sliced_vocc', 'Duration:sliced_vocc', 
                                   'SppR1:sliced_vocc', 'sliced_vocc', 
                                   'Duration:SppR1:mean_nuts', 'Duration:mean_nuts', 
                                   'SppR1:mean_nuts', 'mean_nuts', 
                                  'Duration:SppR1:scaled_invs', 'Duration:scaled_invs', 
                                  'SppR1:scaled_invs', 'scaled_invs'
                                  ))) %>% 
  mutate(sig = '*', sig = replace(sig, sig_stars == ' ', ''))

```

Initial richness: 

* areas of higher species richness experience greater losses (as expected)
* yet over the long term, there is an average of species gains in the coastal areas examined in this study
* I am not sure what I think this means with the richness*duration interaction - high richness does not change the long-term outcome of species richness gain. But I do not think that this makes sense.

* stars over the points indicate these were significantly different from zero.

```{r}

full_rma_all_summary %>% 
  filter(grouping == 'mods') %>% 
  ggplot(data = ., aes(x = estimate, y = driver)) + 
    theme_bw() + 
    geom_point(size = 4) +
    geom_errorbarh(aes(y = driver, xmin = ci_lb, xmax = ci_ub), height = 0, size = 1.5) + 
    geom_text(aes(x = estimate, y = driver, label = sig), hjust = 0.5, vjust = -0.4, size = 8) + 
    geom_vline(xintercept = 0, colour = 'black', linetype = 'dashed') + 
    xlim(c(-0.085, 0.085))

```

Nutrients

* In the short term, sites exposed to high nutrient loading but that have low initial species richness 
experience species gains on average. 
* In areas of high species richness however, 

```{r}

full_rma_all_summary %>% 
  filter(grouping == 'nuts') %>% 
  ggplot(data = ., aes(x = estimate, y = driver)) + 
    theme_bw() + 
    geom_point(size = 4) +
    geom_errorbarh(aes(y = driver, xmin = ci_lb, xmax = ci_ub), height = 0, size = 1.5) + 
    geom_text(aes(x = estimate, y = driver, label = sig), hjust = 0.5, vjust = -0.4, size = 8) + 
    geom_vline(xintercept = 0, colour = 'black', linetype = 'dashed') + 
    xlim(c(-0.17, 0.17))

```


### Attempt to standardize coefficients 

* subset data to include only data that would be included in the model (i.e., exclude data with missing rows)

```{r, eval = FALSE}
sds <- 
  fl_combined %>% 
    filter(!is.na(yi_SppR_ROM) & !is.na(vi_SppR_ROM) & !is.na(mean_invs) & !is.na(sliced_vocc) & !is.na(mean_nuts)) %>% 
    mutate(scaled_invs = mean_invs * 10^-3) %>% 
    summarise(sd_yi = sd(yi_SppR_ROM), 
              sd_duration = sd(Duration), 
              sd_invs = sd(scaled_invs), 
              sd_nuts = sd(mean_nuts), 
              sd_vocc = sd(sliced_vocc), 
              sd_SppR1 = sd(SppR1)
              )

std_full_rma_all <- 
    rma.mv(yi = yi_SppR_ROM, V = vi_SppR_ROM,
           data =   fl_combined %>% 
                    mutate(scaled_invs = mean_invs * 10^-3) %>% 
                    mutate(Duration = Duration * (sds$sd_duration / sds$sd_yi), 
                           scaled_invs = scaled_invs * (sds$sd_invs / sds$sd_yi), 
                           mean_nuts = mean_nuts * (sds$sd_nuts / sds$sd_yi), 
                           sliced_vocc = sliced_vocc * (sds$sd_vocc / sds$sd_yi), 
                           SppR1 = SppR1 * (sds$sd_SppR1 / sds$sd_yi)), 
          random = ~ 1 | Study.ID, 
          mods = ~ Duration * SppR1 * (sliced_vocc + mean_nuts + scaled_invs)
)
std_full_rma_all


fl_combined %>% 
  mutate(scaled_invs = mean_invs * 10^-2) %>% 
  mutate(Duration = Duration * (sds$sd_duration / sds$sd_yi), 
         scaled_invs = scaled_invs * (sds$sd_invs / sds$sd_yi), 
         mean_nuts = mean_nuts * (sds$sd_nuts / sds$sd_yi), 
         sliced_vocc = sliced_vocc * (sds$sd_vocc / sds$sd_yi), 
         SppR1 = SppR1 * (sds$sd_SppR1 / sds$sd_yi)) %>% 
  filter(!is.na(yi_SppR_ROM) & !is.na(vi_SppR_ROM) & !is.na(mean_invs) & !is.na(sliced_vocc) & !is.na(mean_nuts)) %>% 
  select(Duration, scaled_invs, mean_nuts, sliced_vocc, SppR1) %>% 
  cov()

```



#### Events

As expected, in the short-term, sites that were associated with positive events in species richness had increases in species richness. The same was true with studies that were associated with events classified as 'uncertain'.

However, in the long term, event type actually had the opposite effect of what was expected. Events were not classified as press/pulse and this may explain the direction of effects of 'positive' events in the long term.... **except this really doesn't make sense and it is probably things being so context specific. next steps with this could be - 1) seeing what events fall into these categories (but these have been checked and the original predictions do make sense), 2) press/pulse, 3) 

```{r}

localmod <- 
  rma.mv(yi = yi_SppR_ROM, V = vi_SppR_ROM, data = event,
         random = ~ 1 | factor(Study.ID),
         mods = ~ Duration:expected_change + expected_change + 0)
localmod

# Short-term
mk_rma_summary_df(localmod) %>% 
  mutate(driver = factor(c('Negative', 'Positive', 'Uncertain', 'Dur*Negative', 
                      'Dur*Positive', 'Dur*Uncertain'), 
                        levels = c('Uncertain', 'Positive', 'Negative', 
                        'Dur*Uncertain', 'Dur*Positive', 'Dur*Negative'))) %>% 
  filter(driver %in% c('Negative', 'Positive', 'Uncertain')) %>% 
  ggplot(data = ., aes(x = estimate, y = driver)) + 
  theme_bw() +
  geom_point(size = 4) +
  geom_errorbarh(aes(y = driver, xmin = ci_lb, xmax = ci_ub), height = 0, size = 1.5) + 
  geom_vline(xintercept = 0, colour = 'black', linetype = 'dashed') + 
  xlim(c(-0.65, 0.65)) + 
  theme(axis.text.y = element_text(hjust = 1, size = 20), 
      axis.text.x = element_text(size = 20), 
      axis.title = element_text(size = 20))

# Long-term
mk_rma_summary_df(localmod) %>% 
  mutate(driver = factor(c('Negative', 'Positive', 'Uncertain', 'Dur*Negative', 
                      'Dur*Positive', 'Dur*Uncertain'), 
                        levels = c('Uncertain', 'Positive', 'Negative', 
                        'Dur*Uncertain', 'Dur*Positive', 'Dur*Negative'))) %>% 
  filter(driver %in% c('Dur*Negative', 'Dur*Positive', 'Dur*Uncertain')) %>% 
  ggplot(data = ., aes(x = estimate, y = driver)) + 
  theme_bw() +
  geom_point(size = 4) +
  geom_errorbarh(aes(y = driver, xmin = ci_lb, xmax = ci_ub), height = 0, size = 1.5) + 
  geom_vline(xintercept = 0, colour = 'black', linetype = 'dashed') + 
  xlim(c(-0.09, 0.09)) + 
  theme(axis.text.y = element_text(hjust = 1, size = 20), 
      axis.text.x = element_text(size = 20), 
      axis.title = element_text(size = 20))

```