## Local marine diversity change meta-analysis model results

```{r, include=FALSE, cache=TRUE}
source('meta_models.R')
```


```{r, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

options(width=120)
```

```{r, echo=FALSE, cache=FALSE}
library(knitr)
read_chunk("./meta_models.R")
#read_chunk("./plot_effect_sizes.R")

```

### Duration analysis

To test whether local marine species richness has changed over time, we performed a meta-regression on the relationship between the log ratio of species richness between the final and initial time points and study duration. On average, we observed an effect size of `r filter(mod1_output_df, parameter == 'Duration') %>% select(estimate)`, which corresponds to a gain in species richness at a rate of `r filter(mod1_output_df, parameter == 'Duration') %>% select(4)` % per year (Table 1). 

```{r, duration-var-weighted-model-output-table1}
```

```{r, no-event-data-plotted-with-duration-var-weighted-fig1, echo=FALSE, fig.height=6, fig.width=8.5, fig.cap='**Figure 1.** Variance-weighted meta-regression shows an increase in the log ratio of species richness change over time at a rate of species richness gain of 1% per year. Studies could contain data from multiple sites and so studies were modelled as random effects.'}
```

### Cumulative human impacts model 

When cumulative impacts were included in the model, there was an average rate of change per year in the log proportion of species of `r filter(imp_mod_output_df, parameter == 'Duration') %>% select(estimate)` -0.033, which is equivalent to an annual rate of species loss of `r filter(imp_mod_output_df, parameter == 'Duration') %>% select(4)`% across sites (Table 2). While cumulative impact values alone did not predict species richness change in the short term, over the long term (impact * duration interaction), each unit increase in cumulative impact value decreased the rate of species loss per year by `r filter(imp_mod_output_df, parameter == 'Duration:Impact') %>% select(4)`% / (year * impact score) (Table 2, Fig. 2).

Predictions from this model that includes cumulative human impacts show that when cumulative impacts are low, there is a signal of species loss over 15 years (Figs 3 and 4). At intermediate levels of human impact (25th and 50th impact quantiles observed in our data), human impacts alter the rate of change of species richness and produce predictions where no net change is observed over 15 years (Figs 3 and 4). Meanwhile high cumulative impacts (maximum value observed in our data) predict species gains over the long term. However, even when human impacts are high, gains are not predicted to be observed in studies shorter than eight years (Figs 3 and 4). 

```{r, impact-var-weighted-model-output-table2}
```

```{r, impacts-var-weighted-intercept-coefficient-estimates-fig2, fig.cap='**Figure 2.** Coefficient estimates for the relationship of the log-proportion of change in species richness over time, as moderated by cumulative human impacts (Halpern et al 2015). Points represent coefficient estimates and lines represent 95% CI obtained using a variance-weighted meta-regression.'}
```

```{r, impacts-var-weighted-prediction-plots-log-ratio-fig3, fig.height=6, fig.width=8.5, fig.cap='**Figure 3.** Observed log response ratios of proportion of species richness change over 41 years (left) and predicted log response ratios of species richness change over 15 years (right) as moderated by five quantiles of cumulative human impacts observed in our dataset: q0 = 0.89 (blue), q25 = 2.84 (green), q50 = 3.58 (yellow), q75 = 5.04 (orange), q100 = 8.95 (red). Predicted log response ratios are presented for only 15 years, because less than 15% of studies represent durations longer than 15 years (Fig. S2)'}
```

```{r, impacts-var-weighted-prediction-plots-percent-change-fig4, fig.height=6, fig.width=8.5, fig.cap='**Figure 4.** Observed percent change in species richness over 41 years (left) and predicted percent change of species richness change over 15 years (right) as moderated by five quantiles of cumulative human impacts observed in our dataset: q0 = 0.89 (blue), q25 = 2.84 (green), q50 = 3.58 (yellow), q75 = 5.04 (orange), q100 = 8.95 (red). Predicted log response ratios are presented for only 15 years, because less than 15% of studies represent durations longer than 15 years (Fig. S2).'}
```

#### Our results in the global context of cumulative human impacts

Globally the impact values range from 0 to >15. In our analysis, these impact values ranged between `r no_event %>% filter(!is.na(yi_SppR_ROM) & !is.na(vi_SppR_ROM) & !is.na(mean_imps)) %>% summarise(min(mean_imps))` - `r no_event %>% filter(!is.na(yi_SppR_ROM) & !is.na(vi_SppR_ROM) & !is.na(mean_imps)) %>% summarise(max(mean_imps))`

Fifty percent of our studies have cumulative human impact values between `r quantile(no_event$mean_imps, probs = c(0.25, 0.75), na.rm = TRUE)[[1]] %>% round(., digits = 1)` and `r quantile(no_event$mean_imps, probs = c(0.25, 0.75), na.rm = TRUE)[[2]] %>% round(., digits = 1)`. This analysis highlights how biases in our sampling of local communities can obscure effects of human impacts on local scale species richness change. If this sampling is representative of studies used in previous analyses, they do not represent the spread of human impacts affecting marine communities.

```{r, cumulative-impacts-freq-dist-for-var-weighted-dataset-fig5, fig.cap='**Figure 5.** Frequency distribution of cumulative human impacts across the data used for the variance-weighted meta-regression'}
```

```{r}
# global cumulative human impacts frequency distribution goes here to compare 
# with what is in the data.
```

### Specific drivers model 

Accounting for cumulative human impact values suggests that, as expected, species richness changes are context dependent. These results suggest that human impacts moderate the rate at which species richness changes. However, the cumulative human impact values summarise 19 different human impacts in marine ecosystems (Halpern et al. 2015). We ask whether the direction and magnitude of local species richness change can be more specifically attributed to three primary global drivers of diversity change. In particular, temperature change, nutrient addition, and species invasions are three drivers that have been associated with changes in local communities (Murphy and Romanuk 2014, ...) and are three of the data layers that have been included in the calculation of cumulative human impact values. We have used the invasion potential (quantified using global shipping tonnage as a proxy for propagule pressure) and nutrient addition data layers aggregated by Halpern et al. (2015) in our analysis, in addition to the decadal rate of linear temperature change calculated using the Hadley Met Centre sea surface temperature data. 

The inclusion of additional and specific drivers of global change show changes in species richness over time and show that these changes differ in both direction and magnitude depending on the driver and study duration (Table 3, Fig. 6). On average, there was a signal of species gains over time, at a rate of `r filter(drivers_mod_output_df, parameter == 'Duration') %>% select(4)` percent of starting richness per year (Table 3). Linear temperature change (5.33 % per ˚C / decade) and nutrient addition (1.3 % per tonne of nutrients / km^2 - this seems really really high) were also both correlated with gains in species richness in the short term (Table 3, Fig. 6). At the current decadal rate of sea surface temperature (`r 0.13 * (5 / 9)` ˚C / decade), this would be `r (filter(drivers_mod_output_df, parameter == 'Duration') %>% select(4)) * 0.13 * (5 / 9)` percent increase due to temperature change. 

Over time, all three drivers affected the rate of local species richness change (Table 3, Fig. 6 left). Invasives increase the rate of species gains (0.12 % per thousand tonnes of shipping tonnage) while, unlike in the short term, linear temperature change and nutrient addition decreased species richness over time (Fig. 6 right). Figures 7, 8, and 9 demonstrate how these drivers affect species richness over 15 years, assuming that each driver is held constant at the median level observed in our data. 

```{r, include=FALSE}
# URL to webpage that had current decadal rate of temperature change.
# https://www3.epa.gov/climatechange/science/indicators/oceans/sea-surface-temp.html
```

```{r, drivers-var-weighted-model-output-df-scaled-table3}
```

```{r, drivers-var-weighted-intercept-scaled-par-est-plot-short-long-breakdown-fig6, fig.height=6, fig.width=9, fig.cap = '**Figure 6.** The relationship of the log-proportion of change in species richness over time, as moderated by three drivers of global change, invasives (propagule pressure), nutrient addition, and LTC (the decadal rate of linear temperature change). Points represent standardised coefficient estimates and lines represent 95% CI obtained using a variance-weighted meta-regression.'}
```

--------------------------------------------------------------------------------

#### Predictions from the multiple drivers model

--------------------------------------------------------------------------------

```{r, full-drivers-model-var-weighted-invasives-predictions-with-dists-fig7, fig.height=6.5, fig.width=8.5, fig.cap='**Figure 7.** Predicted change in the log-proportion of change in species richness over time as moderated by invasion potential over 15 years (Left). Predictions were obtained using a variance-weighted meta-regression from the full drivers model: LR ~ Duration * (invasion potential + nutrient addition + linear temperature change). Nutrient addition and linear temperature change were held constant at the median values of these two drivers found observed in our dataset. Shaded areas represent 95% confidence intervals. Cumulative frequency distributions (top right) and frequency histograms (bottom right) invasion potential values observed in the data used for the variance-weighted meta-regression. Shipping tonnage was used as a proxy for invasion potential.'}
```

--------------------------------------------------------------------------------


```{r, full-drivers-model-var-weighted-nutrients-predictions-with-dists-fig8, fig.height=6.5, fig.width=8.5, fig.cap='**Figure 8.** Predicted change in the log-proportion of change in species richness over time as moderated by nutrient addition over 15 years. Predictions were obtained using a variance-weighted meta-regression from the full drivers model: LR ~ Duration * (invasion potential + nutrient addition + linear temperature change). Invasion potential and linear temperature change were held constant at the median values of these two drivers found observed in our dataset. Shaded areas represent 95% confidence intervals. Cumulative frequency distributions (top right) and frequency histograms (bottom right) nutrient addition values observed in the data used for the variance-weighted meta-regression.'}
```

--------------------------------------------------------------------------------


```{r, full-drivers-model-var-weighted-ltc-predictions-with-dists-fig9, fig.height=6.5, fig.width=8.5, fig.cap='**Figure 9.** Predicted change in the log-proportion of change in species richness over time as moderated by nutrient addition over 15 years. Predictions were obtained using a variance-weighted meta-regression from the full drivers model: LR ~ Duration * (invasion potential + nutrient addition + linear temperature change). Invasion potential and nutrient addition were held constant at the median values of these two drivers found observed in our dataset. Shaded areas represent 95% confidence intervals. Cumulative frequency distributions (top right) and frequency histograms (bottom right) linear temperature change observed in the data used for the variance-weighted meta-regression.'}
```


--------------------------------------------------------------------------------

#### Driver interactions

Interactions between changing temperature and invasive species colonisation and changing temperature and nutrient addition have been predicted theoretically and are supported by observational (Sorte et al 2010 (invs), ...) and experimental data (Binzer et al 2012 (nuts), ...). We tested whether the effects of these interactions between temperature, propagule pressure, and nutrient addition were observed in our data. We did not observe an effect of these interactions in our data, however, this may be due to low power of using only studies (n = 24) that had sampling variances (Table 5). 

```{r, interactions-var-weighted-model-output-table4}
```

--------------------------------------------------------------------------------

#### Sample size weighted results summary

Unfortunately, the results from the variance-weighted meta-analysis differ from the results of both the sample size-weighted analysis and the unweighted analysis. In these sample size-weighted analyses, the number of replicates for each site was used as a proxy for precision of the species richness change estimate. Therefore, sites with higher replication had higher weights in the analysis. We did this because there were many studies for which there were no variances provided, which limited our sample size in the variance-weighted analysis. We triple our sample size by using a sample-size meta-regression (Table 5).

In the sample size-weighted meta-regressions, no trends in species richness change were observed ~~in the LR ~ Duration or LR ~ Duration\*Impact models (Tables 6 and 7). In the full drivers model (LR ~ Duration \* (I + N + LTC)), the only observed trend, was long term positive effect of invasive potential on the rate of species richness change (Table 8, Fig. 10). This same effect was observed in the variance-weighted meta-regression (Table 3, Fig. 6).~~ in any of the models (Tables 6-13, Figs. 10 & 11). (This was where I made the mistake in the code...)

~~In the drivers interaction model, where linear temperature change interacted with invasion potential and nutrient addition, the variance-weighted meta-regression showed no significant trends (Table 4). However, in the sample size-weighted meta-regression, the invasion potential\*linear temperature change interaction was associated with species losses in the short term and the linear temperature change\*nutrient addition interaction was associated with species gains in the long term (Table 9).~~

```{r, sample-size-diffs-based-on-mod-weighting-comparison-table5}

```{r, duration-ss-weighted-model-output-df-table6}
```

```{r, impact-ss-weighted-model-output-df-table7}
```

```{r, drivers-ss-weighted-model-output-df-scaled-table8}
```

```{r, drivers-ss-weighted-intercept-scaled-par-est-plot-short-long-breakdown-fig10,  fig.height=6, fig.width=9, fig.cap = '**Figure 10.** The relationship of the log-proportion of change in species richness over time, as moderated by three drivers of global change, invasives (propagule pressure), nutrient addition, and LTC (the decadal rate of linear temperature change). Points represent standardised coefficient estimates and lines represent 95% CI obtained using a sample size-weighted meta-regression.'}
```

```{r, drivers-interactions-ss-weighted-model-output-df-scaled-table9}
```

```{r, drivers-ss-weighted-intercept-scaled-par-est-plot-short-long-breakdown-fig11,  fig.height=6, fig.width=9, fig.cap = '**Figure 11.** The relationship of the log-proportion of change in species richness over time, as moderated by three drivers and of global change, invasives (propagule pressure), nutrient addition, and LTC (the decadal rate of linear temperature change) and their interaction. Points represent standardised coefficient estimates and lines represent 95% CI obtained using a sample size-weighted meta-regression.'}
```

--------------------------------------------------------------------------------


#### Unweighted results summary

```{r, duration-unweighted-model-output-df-table10}
```

```{r, impact-unweighted-model-output-df-table11}
```

```{r, drivers-unweighted-model-output-df-table12}
```

```{r, interactions-unweighted-model-output-df-table13}
```
--------------------------------------------------------------------------------

